Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-03-04 papers/Papers1234/sec-strong-coupling.tex
Start writing about the shell structure figure

In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
corresponding to \(d\cool = R_0\) (thick blue line) and
\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
thickness in the efficient cooling case.  In this context, \(n_0 = n\)
and \(n_2 = n\shell\), so that \(h_0\) follows from
equations~\eqref{eq:shocked-shell-column}
and~\eqref{eq:isothermal-shell-density} as
\begin{equation}
  \label{eq:strong-cooling-h0}
  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
\end{equation}
The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
maximum in the cooling coefficient \(\Lambda(T)\) around
\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
blue line, radiative cooling is so efficient that the bow shock can be
considered isothermal, and so the shell is dense and thin (at least,
in the apex region).  It can be seen that the ionization front
trapping always occurs at densities larger than this, which justifies
the use of equation~\eqref{eq:isothermal-shell-density} in the
previous section.  For bows with outer stream densities below the
thick blue line, cooling is unimportant and the bow shock can be
considered non-radiative.  In this case the shell is thicker than in
the radiative case,
\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
  An approximate value can be found from
  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
  Consideration of the slight increase in density between the shock
  and the contact/tangential discontinuity reduces this value by 5--10\%.} %
For bows with outer stream densities between the two blue lines,
cooling does occur, albeit inefficiently, so that the shell thickness
is set by \(d\cool\) rather than \(h_0\).

>>>>

In Figure~\ref{fig:zones-v-n-plane} we show curves calculated from
equations~\eqref{eq:shock-n-jump} to~\eqref{eq:heating-coefficient},
corresponding to \(d\cool = R_0\) (thick blue line) and
\(d\cool = h_0\) (thin blue line), where \(h_0\) is the shell
thickness in the limit of instantaneous cooling.  In this context,
\(n_0 = n\) and \(n_2 = n\shell\), so that \(h_0\) follows from
equations~\eqref{eq:shocked-shell-column}
and~\eqref{eq:isothermal-shell-density} as
\begin{equation}
  \label{eq:strong-cooling-h0}
  h_0 = \tfrac34 \M_0^{-2} R_0 \ .
\end{equation}
The bends in the curves at \(v \approx \SI{50}{km.s^{-1}}\) are due to the
maximum in the cooling coefficient \(\Lambda(T)\) around
\(\SI{e5}{K}\).  For bows with outer stream densities above the thin
blue line, radiative cooling is so efficient that the bow shock can be
considered isothermal, and so the shell is dense and thin (at least,
in the apex region).  It can be seen that the ionization front
trapping always occurs at densities larger than this, which justifies
the use of equation~\eqref{eq:isothermal-shell-density} in the
previous section.  For bows with outer stream densities below the
thick blue line, cooling is unimportant and the bow shock can be
considered non-radiative.  In this case the shell is thicker than in
the radiative case,
\(h\shell/R_0 \approx \text{\numrange{0.2}{0.3}}\).\footnote{%
  An approximate value can be found from
  equation~\eqref{eq:shocked-shell-column} by substituting \(n = n_0\)
  and \(n\shell \approx n_1\), then using equation~\eqref{eq:shock-n-jump}.
  Consideration of the slight increase in density between the shock
  and the contact/tangential discontinuity reduces this value by 5--10\%.} %
For bows with outer stream densities between the two blue lines,
cooling does occur, albeit inefficiently, so that the shell thickness
is set by \(d\cool\) rather than \(h_0\).

\subsection{Axial structure of bow shells}
\label{sec:axial-structure-bow}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/shell-profiles}
  \caption{Profiles of physical variables along the axis of bow shells
    for (a)~wind-supported bow shock; (b)~radiation-supported bow
    wave, and (c)~radiation-supported bow shock.  In all cases, a
    stream velocity of \SI{30}{km.s^{-1}} and an equilibrium ionized
    sound speed of \SI{10}{km.s^{-1}} are assumed.}
  \label{fig:axial-structure}
\end{figure}

In the shell of a wind-supported bow shock, the gas density is highest
at the contact discontinuity, but this is no longer true for
radiation-supported bows, as illustrated in
Figure~\ref{fig:axial-structure}.  For the optically thin RBW case,
equations~\eqref{eq:rad-accel} to~\eqref{eq:rad:R0} can be combined to
give the radial dependence of the stream velocity as it approaches the
star:
\begin{equation}
  \label{eq:v-RBW-ballistic}
  v(R) = \left( 1 - \frac{R_{**}}{R} \right)^{1/2} v_\infty \ .
\end{equation}
This ballistic approximation (shown by the dashed red line in
Fig.~\ref{fig:axial-structure}b) predicts that the velocity smoothly
decreases to zero at \(R = R_{**}\).  However, although this is valid
in the limit of high Mach number, it ignores the effects of gas
pressure and so becomes invalid once the stream velocity falls close
to the sound speed.

\section{Discussion}
\label{sec:discussion}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/zones-v-n-plane-Weak}
  \caption{As Fig.~\ref{fig:zones-v-n-plane}, but for a weak-wind
    O~star, similar to the sample observed by \citet{Martins:2005b}.
    For this star, radiation-supported bow waves (gray shading) occur
    over a much larger region of parameter space than for a
    normal-wind star of the same spectral type
    (see Fig.~\ref{fig:zones-v-n-plane}b).}
  \label{fig:O-weak-wind}
\end{figure}

Hot stars, comparison with expected velocities and densities.

Expected velocities.  There are cases of high velocities, e.g., AE~Aur, but they are probably rare. \citep{Renzo:2018a}
In cases, where proper motions are measured, they are often low.

Metallicity dependence of wind strength. RBW more likely at lower metallicities.

Weak wind stars - repeat the 20 Msun case, but for a much lower \(\eta\wind\)

Cool stars, comparison with observed densities (Betelgeuse, for
instance). Other ones in \citep{Cox:2012a}.

Prospects for observation in LMC: 1 parsec = 4 arcsec, so need JWST to get most of them.
